\textbf{Using the MSU Thesis Class}

### 2022-08-24 docs/msu-thesis.tex
v3.6 added better support for Key to Abbreviations; changed \onelineskip to be fontsize since thesis office doesn't know how to measure

\def\msuversion{3.5b}
\def\msudate{2022/08/19}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

Another common kind of list is a List of Abbreviations. The thesis office seems to want to call this “Key to Abbreviations”.  To add such a list, you need to do the following:

\begin{quote}
\begin{lstlisting}
\clearpage
\chapter*{Key to Abbreviations}
\vspace{\cftparskip}
\addcontentsline{toc}{chapter}{Key to Abbreviations}
Your list of abbreviations here.
\end{lstlisting}
\end{quote}

@@

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version, and Florent Chervet for the \pkg{hyperref}\ code. Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk Jung, Adam Liter, Vanessa Maldonado, William Muir, Alicia Parrish, Neil ver Planck, Giacomo Romanini, William Sands, Adam Soliman, Erik Stitt,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Ali Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.

>>>>

\def\msuversion{3.6}
\def\msudate{2022/08/23}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

\subsection{Key to Abbreviations}
Another common kind of list is a List of Abbreviations. The thesis office seems to want to call this “Key to Abbreviations”.  The thesis office seems to think that these should be formatted identically to other lists, even though they are not really contents lists. Because of this I have added a built-in |\listofabbreviations| and a helper macro to add elements to the list. The basic idea is the following: for each abbreviation/symbol you add to the list use the command |\msuabbrev{<abbreviation>}{<explanation>}|. This command takes two arguments, the first being the abbreviation itself, and the second the explanation of the abbreviation. For example, for a list of abbreviations containing the abbreviations MSU and MIT we would use the following code. At the end of all of the |\msuabbrev| commands, there is the |\listofabbreviations| command which actually prints the list. The list is not automatically sorted, so you need to add abbreviations with |\msuabbrev| in exactly the order you want them to appear in the list.

\begin{quote}
\begin{lstlisting}
\msuabbrev{MIT}{Massachusetts Institute of Technology}
\msuabbrev{MSU}{Michigan State University}
\clearpage
\listofabbreviations
\end{lstlisting}
\end{quote}
\subsubsection{Summary of abbreviation commands}
In addition to the |\msuabbrev| command, there are a few other commands to change the format of the the |\listofabbreviations| as shown in Table~\ref{abbrev}.

\begin{table}[htpb]
\centering
\begin{tabularx}{.8\textwidth}{>{\ttfamily}lX}
\toprule
{\bs msuabbrev\{<abbreviation>\}\{<explantion>\}} & Add an abbreviation to the list.\\
{\bs listofabbreviations } & Print the list of abbreviations.\\
{\bs msuabbrevfont} & Format of the abbreviation itself (default is \texttt{\bs bfseries}).\\
{\bs msuabbrevdelim\{\}} &  Add a delimiter if you need (default is \texttt{\{\}}).\\
{\bs msuabbrevwidth\{\}} &  Set the width of the abbreviation column (default is \texttt{.75in}).\\
\bottomrule
\end{tabularx}
\caption{List of abbreviation commands}\label{abbrev}
\end{table}

@@

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version, and Florent Chervet for the \pkg{hyperref}\ code. Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk Jung, Adam Liter, Vanessa Maldonado, William Muir, Alicia Parrish, Neil ver Planck, Nick Rekuski, Giacomo Romanini, William Sands, Adam Soliman, Erik Stitt,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Ali Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.
